---
title: "fastqR_usage"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{fastqR_usage}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(fastqR)

```
Background
==========

FastQ files are composed of entries consisting of 4 lines
1. ID line. Starts with an @ symbol. Sequence ID is anything after that. IDs should be unique
2. Sequence line - should be a string of G/A/T/C/N bases
3. Mid line - starts with a + and are generally ignored.
4. Quality line. Should be a string of characters the same length as the sequence.

An example of a fastq file contain 2 sequence records would be:

@1HWUSI-EAS460:44:661VRAAXX:2:1:15253:1153
GCCNGGCTATGCAAGCAGGCTGCAGTGTGGATATAGTCGT
+1HWUSI-EAS460:44:661VRAAXX:2:1:15253:1153
???#;ABAAAHHHHGHFGDHEG@GG@GDGGB>DDDGBDD=
@2HWUSI-EAS460:44:661VRAAXX:2:1:17398:1153
CAGNGAATCCTTGAGGCACCTTCTCTTATAAAAACA
+2HWUSI-EAS460:44:661VRAAXX:2:1:17398:1153
BBB#BFFFEFHHHHHDHHHHHHHHHHHHHHHHHHHH

read_fastq
==========

read_fastq reads a .fq format file and returnsa tibble with one row per fastq entry where the columns are:

1. ID (the sequence ID from the first line, minus the @)
2. Bases (the bases from the second line)
3. Qualities (the quality string from the 4th line)
4. GC (the GC content of the bases)


```{r}
head(read_fastq(system.file("good.fq", package = "fastqR")))
```

gc_content
==========

Take in a vector of DNA sequence strings and return a vector of %GC values (what
percentage of the bases are G or C). 

```{r}

gc_content("GAGAGCGGCTT")

```
decode_qualities
================

Converts a scalar string of quality values into a vector of Phred scores.

*Phred score = ASCII value of letter - offset*

```{r}

decode_qualities("???#;ABAAAH")

```

